---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(safeRview) # load package's functions inside the README.Rmd file
```

# safeRview 📦

<!-- badges: start -->
<!-- badges: end -->

> An R package for summarizing and visualizing clinical trial adverse event (AE) data.

**Note:** This package is a portfolio project built to demonstrate core skills in R package development, data visualization, and statistical analysis within a pharmaceutical context. It is the foundation for an interactive Shiny dashboard.

---

## Installation

You can install the development version of safeRview from [GitHub](https://github.com/rodb76/safeRview) with:

```r
# install.packages("devtools")
devtools::install_github("rodb76/safeRview")
```

---

## Example Usage

This package contains all the functions needed to go from raw CDISC-like data to publication-ready plots.

```{r summarize}

# 1. Load the example datasets built into the package
data(adsl)
data(adae)

# 2. Create the summary analysis table
ae_table <- summarize_ae_data(adsl, adae)

print(head(ae_table))
```


# 3. Create a bar chart of the Top 10 AEs
```{r barchart, echo = FALSE}
p_bar <- plot_ae_barchart(ae_table, top_n = 10)

print(p_bar)
```

# 4. Create a volcano plot comparing two arms

```{r volcano, echo = FALSE}
p_volcano <- plot_ae_volcano(
  adsl = adsl,
  adae = adae,
  treatment_arm = "A: Drug X",
  comparator_arm = "B: Placebo"
)

print(p_volcano)
```




---

## Core Components

This package demonstrates several key software development practices:

* **`data-raw/DATA.R`**: The script used to generate and process the `adsl.rda` and `adae.rda` example datasets.
* **`R/`**: Contains all core functions, separated by concern:
    * `summarize_ae.R`: Holds the `tidyverse`-based analysis function (`summarize_ae_data`).
    * `plot_ae.R`: Holds the `ggplot2` visualization functions (`plot_ae_barchart`, `plot_ae_volcano`).
* **Documentation**: All functions are documented using `roxygen2`, which generates the package `NAMESPACE` and help files (`.Rd`).
* **Testing**: The package includes a full suite of unit tests in the `tests/testthat/` directory to validate the analysis and plotting functions. You can run these locally with `devtools::test()`.

---

## Next Steps: Shiny Dashboard

The next phase of this project is to build an interactive Shiny application that uses this package as its analytical engine. This will demonstrate skills in:

* Shiny UI/Server development
* Reactive programming
* Interactive plotting with `plotly`
* Application deployment on `shinyapps.io`


